Supplemental Materials, Methods and Results

### 2021-05-09 supp.Rmd
Adding in and correcting local adaptation..includes body region

  # Fit the interaction model
  DispBgrdAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC_inter)

  # Fit the main effect model
  DispBgrdAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC)

  # Doesn't look like an interaction, so test.
  anova(DispBgrdAC_inter, DispBgrdAC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

  # Planned contrast. Fit the model in a slightly different way
  DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
  DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd) 
  summary(DisplayBgrd_pop_back)

  robust_DisplayBgrd_pop_back <- clubSandwich::conf_int(DisplayBgrd_pop_back, cluster = DisplayBgrd$ID, vcov =  "CR2")

>>>>

  # Fit the interaction model
  DispBgrdAC <- lmer(dL ~ Population  + Background_pop + BodyRegion + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt_DispBgrdAC <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

  BodyRegion_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(4:6), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

  # Planned contrast. Fit the model in a slightly different way ********************** UP TO HERE
  DisplayBgrd$pop_back_region <- with(DisplayBgrd, interaction(Population, Background_pop, BodyRegion))
  DisplayBgrd_pop_back_region <- lmer(dL ~ pop_back_region + (1|ID), data = DisplayBgrd) 
  summary(DisplayBgrd_pop_back_region)

  robust_DisplayBgrd_pop_back_region <- clubSandwich::conf_int(DisplayBgrd_pop_back_region, cluster = DisplayBgrd$ID, vcov =  "CR2")
